### 2017-05-11 manuscript/usses_water_ms.Rmd
adds little abstract, for context

\begin{abstract}
Summarize it here
\vspace{2em}
\end{abstract}

>>>>

\begin{abstract}
Precipitation is predicted to become more variable in the western U.S., meaning years of above and below average precipitation will become more common.
Such periods of drought and deluge could become major drivers of plant community dynamics and ecosystem functioning.
We used drought and irrigation treatments (50\% decrease/increase) to see how a sagebrush steppe plant community in Idaho will respond to future climate changes.
The ecosystem was suprisingly resistant to both drought and irrigation.
Aboveground net primary productivity (ANPP) and its temporal stability did no differ among treatments.
The similarity of ecosystem functioning was not due to shifts at the plant community level, where species compositions and species synchrony, an important driver of ecosystem stability, among treatments were similar.
However, ANPP does appear to be diverging among treatments with time, even though the effect is not significant.
At least in the short-term, this sagebrush steppe ecosystem is resistant to increases and decreases in annual precipitation.

\vspace{2em}

\emph{Key words: drought, aboveground net primary productivity, ecosystem stability, climate change, species synchrony}
\end{abstract}
